Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-07 kappa.tex
Update figure captions.

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{Indicators of climatic fluctuations during the last 800\,ka of
           Earth history.
           \textbf{(a)} Benthic oxygen isotope \chem{\delta^{18}O} record from
           a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies reconstructed from a central
           Antarctic ice core \citep[EPICA,][]{Jouzel.etal.2007}.
           The grey boxes indicate the approximate time span of the last
           glacial period of 110 to 10\,ka, which corresponds to our period of
           interest in the present thesis.}
  \label{fig:paleo-timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present, and \textbf{(b)} during the last
           glacial maximum \citep{Ehlers.Gibbard.2007}. Coastlines and present
           glaciers are made with Natural Earth \citep{Patterson.Kelso.2014}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-northamerica}}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas covered by the Cordilleran (CIS), Laurentide (LIS), Innuitian
           (IIS) and Greenland (GIS) ice sheets during the last glacial maximum
           \citep[21.4 to 16.8\,cal\,\chem{^{14}C}\,kyr\,BP][]{Dyke.2004}.
           The rectangular box delimits the model domain used throughout this
           thesis and on which most figures were drawn. The background
           map consists of ETOPO1 \citep{Amante.Eakins.2009} and Natural Earth
           Data \citep{Patterson.Kelso.2014}.
           \todo{Mark palaeo-ice sheets on the map.}}
  \label{fig:map-northamerica}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-cordillera}}
  \caption{North-oriented topographic map of the northern American Cordillera.
           Cumulative last glacial maximum ice cover from \citet{Dyke.2004}.
           The background map consists of ETOPO1 \citep{Amante.Eakins.2009}
           and Natural Earth Data \citep{Patterson.Kelso.2014}.
           \todo{Mark the main reliefs. Add model domain?}}
  \label{fig:map-cordillera}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-alaska-range}}
  \caption{The Alaska Range hosts several of the highest peaks in the North
           American Cordillera. Despite this fact and its northerly location,
           its North slopes hosts relatively small glaciers only, which had not
           been much more extensive during the Last Glacial Maximum
           \citep{Kaufman.Manley.2004}, indicating dry climate conditions.
           The Alaska Range is rapidly eroding, as shown by landslide-covered
           valley sides on this photograph.}
  \label{fig:photo-alaska-range}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Model variables. \todo{This is an old figure which does not match
           with notations in use, just to give an idea. Redraw.}}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{The SIA and SSA. From \citet{Winkelmann.etal.2011}. \todo{Redraw.}}
  \label{fig:model-siassa}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-northamerica}}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas covered by the Cordilleran (CIS), Laurentide (LIS), Innuitian
           (IIS) and Greenland (GIS) ice sheets during the last glacial maximum
           \citep[21.4 to 16.8\,cal\,\chem{^{14}C}\,kyr\,BP,][]{Dyke.2004}.
           The rectangular box delimits the model domain used in all simulation
           and most figures of this thesis. The background
           map consists of ETOPO1 \citep{Amante.Eakins.2009} and Natural Earth
           Data \citep{Patterson.Kelso.2014}.}
  \label{fig:map-northamerica}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-cordillera}}
  \caption{Topographic map of the northern American Cordillera, oriented north.
           Cumulative last glacial maximum ice cover \citep{Dyke.2004} is
           marked in red, and the model domain in black.
           The background map consists of ETOPO1 \citep{Amante.Eakins.2009}
           and Natural Earth Data \citep{Patterson.Kelso.2014}.}
  \label{fig:map-cordillera}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-alaska-range}}
  \caption{The Alaska Range hosts several of the highest peaks in the North
           American Cordillera. Despite this fact and its northerly location,
           its north slope hosts relatively small glaciers only, which had not
           been much more extensive during the Last Glacial Maximum
           \citep{Kaufman.Manley.2004}, indicating dry climatic conditions.
           The Alaska Range is rapidly eroding, as shown by landslide-covered
           valley sides on this photograph.}
  \label{fig:photo-alaska-range}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.
           \todo{Redraw.}}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Sketch of notations used for the main variables of the ice sheet
           model.}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{Shallow Ice Approximation (SIA) and Shallow Shelf Approximation
           (SSA) velocities in PISM. From \citet{Winkelmann.etal.2011}.
           \todo{Redraw.}}
  \label{fig:model-siassa}
\end{figure}
